Behavior Driven Development in Haskell

### 2012-10-20 paper.tex
Derive Show instance for Small
Update example code

\begin{quote}
\small
\begin{verbatim}
newtype Small = Small Int

@@

fibs = 0 : 1 : zipWith (+) fibs (tail fibs)

@@

import Test.QuickCheck
import Test.Hspec.ShouldBe

@@

-- small non-negative numbers
newtype Small = Small Int

@@

spec = do
  describe "fib" $ do
    it "calculates arbitrary Fibonacci numbers" $ do
      property $ \(Small n) ->
        fib n == fib (n + 2) - fib (n + 1)

>>>>

\begin{quote}
\small
\begin{verbatim}
newtype Small = Small Int
  deriving Show

@@

fibs :: [Integer]
fibs = 0 : 1 : zipWith (+) fibs (tail fibs)

@@

import Test.Hspec
import Test.QuickCheck

@@

-- small non-negative integers
newtype Small = Small Int
  deriving Show

@@

spec :: Spec
spec = do
  describe "fib" $ do
    it "calculates arbitrary Fibonacci numbers" $ do
      property $ \(Small n) ->
        fib n == fib (n + 2) - fib (n + 1)
